---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

_This repository is an activity completed by [Zehui Yin](https://zehuiyin.github.io/) for the course [GEOG 712 Reproducible Research Workflow with GitHub and R](https://academiccalendars.romcmaster.ca/preview_course.php?catoid=55&coid=274877), taught by [Dr. Antonio Paez](https://experts.mcmaster.ca/display/paezha) in Fall 2024._

# Research Interest

My research interests lie in __spatial analysis__, __travel behaviour__, __public transit__, and __shared mobility__. I am particularly interested in using an _evidence-based approach_ and _quantitative methods_, such as _econometrics_, to examine transportation systems. From 2022 to 2024, I worked as a research assistant in the [Suburban Mobilities Cluster](https://www.utsc.utoronto.ca/suburban-mobilities/) within the Department of Human Geography at the University of Toronto Scarborough. During this time, I conducted _surveys_ and _network_ data analysis to explore transportation _accessibility_, _equity_, and _justice_ in suburban areas, particularly in Scarborough, Ontario, under the supervision of [Dr. Steven Farber](https://www.utsc.utoronto.ca/geography/steven-farber), [Dr. Andre Cire](https://utsc.utoronto.ca/mgmt/andre-cire), and [Dr. Ignacio Tiznado-Aitken](https://tiznadoaitken.cl/). My works on analyzing transport investment priorities among Scarborough residents and cycling comfort levels on different street types in Toronto were both funded by the [University of Toronto Excellence Award](https://www.utsc.utoronto.ca/research/university-toronto-excellence-award). I have also collaborated on several shared micromobility projects with [Dr. Xiang Yan](https://www.essie.ufl.edu/people/name/xiang-yan/) from the University of Florida. In these projects, I conducted econometric modelling and spatial analysis to investigate the travel behaviour and spatiotemporal patterns of shared e-scooter usage in Washington, DC, and Los Angeles.

# Favourites

## Favourite Music

<!---
Generated using https://www.tablesgenerator.com/
--->

1. Like the Wind (Simplified Chinese: 像风一样) by Joker Xue (Simplified Chinese: 薛之谦)
2. Express Your Feelings (Simplified Chinese: 聊表心意) by Sara (Xijun) Liu (Simplified Chinese: 刘惜君) and Joker Xue (Simplified Chinese: 薛之谦)
3. The City (Simplified Chinese: 牧马城市) by Buyi Mao (Simplified Chinese: 毛不易)
4. The Brightest Star in the Night Sky (Simplified Chinese: 夜空中最亮的星) by Escape Plan (Simplified Chinese: 逃跑计划)
5. The Final Battle (Simplified Chinese: 最后的战役) by Jay Chou (Simplified Chinese: 周杰伦)

## Favourite Equation

The equation below shows the OLS estimators in matrix form.

$$
\hat{\beta}=(X'X)^{-1}X'y
$$

## Favourite Artists

| Name              | Achievements              |
|-------------------|---------------------------|
| Vincent van Gogh  | The Starry Night          |
| Pablo Picasso     | Guernica                  |
| Leonardo da Vinci | Mona Lisa                 |
| Johannes Vermeer  | Girl with a Pearl Earring |
| Claude Monet      | Impression, Sunrise       |

# A Chunk of Code

```{r}
# run a linear regression with the built-in dataset mtcars
m1 <- lm(mpg ~ cyl + hp + wt + vs + am, 
         data = mtcars)

# save the model results to data folder
saveRDS(m1, file = "./data/m1.rds")


# summarize the regression results
summary(m1)
```

# Folder Structure
<!---
Generated using https://tree.nathanfriend.io

Text used:

- data
  - ...
- data-raw
  - data_source.csv
  - ...
- images
  - hamilton_CT.png
- renv
  - ...
- _dependencies.R
- my-GEO712-repository.Rproj
- README.md
- README.Rmd
- renv.lock
- ...
--->

```
.
├── data/
│   └── ...
├── data-raw/
│   ├── data_source.csv
│   └── ...
├── images/
│   └── hamilton_CT.png
├── renv/
│   └── ...
├── _dependencies.R
├── my-GEO712-repository.Rproj
├── README.md
├── README.Rmd
├── renv.lock
└── ...
```

The folder structure is illustrated in the diagram above.

- The `data/` folder stores processed data after analysis or cleaning.
- The `data-raw/` folder contains read-only raw data for the project. Within this folder,`data_source.csv` is a data table that includes the source information for all raw data, such as the download URL and the access date.
- The `images/` folder is designated for storing images, figures, and photos.
- The `_dependencies.R` file is used to add packages to the lockfile that are not automatically included.

# Project Data Analysis

- List the data that you expect to use, collect or create in your project. Identify if you are generating or collecting the data and if you are using existing datasets?

*I plan to compute a spatial accessibility index for transit access to grocery stores in Hamilton at the Census Tract level, similar to the one computed by [Statistics Canada](https://www150.statcan.gc.ca/n1/pub/27-26-0001/272600012023001-eng.htm). To achieve this, I will use the Hamilton Street Railway’s General Transit Feed Specification (GTFS) data, the OpenStreetMap road network, supermarket/grocery store locations from OpenStreetMap, and Census Tract spatial data from Statistics Canada through [Census Mapper](https://censusmapper.ca/api). Therefore, I will be utilizing existing datasets.*

- Are there legal or ethical restrictions that you will need to address?

*Since I am only using open data, there are minimal legal and ethical concerns. Open Hamilton allows me to copy, modify, publish, translate, adapt, distribute, or otherwise use the data in any medium, mode, or format for any lawful purpose. Similarly, OpenStreetMap grants permission to copy, distribute, transmit, and adapt their data. Both sources require proper credit or acknowledgment as the data providers.*

- Go through the Quick Hits for Data Management and identify possible strategies to build and protect the value of your data.  

  - Where will you keep raw data and how will you back it up?

  *All the raw data I use will be kept in the `data-raw/` folder and pushed to GitHub, while also being stored locally on my laptop. Additionally, I’ll keep a zipped folder of all the raw data on an external hard drive as a physical backup.*
      
  - What file formats do you anticipate your data will be in? Are the formats open or can they be converted to open formats?

  *I anticipate my data will be in `geojson`, `csv`, `GTFS`, and `PBF` formats. These are all open formats, and there are open-source and free tools available to work with each of them.*

  - Create a File naming convention for your project data

  *I will use lowercase words and underscores for all project data, except for established acronyms like “GTFS,” where I will use capitalized characters.*
      
  - What standards are relevant to your project? List any existing standards or best practices in use in your field or in your lab? This could include instrument procedures or file management standards. What standards might you want to create to help you manage your data?

  *Versioning is crucial when conducting spatial analysis or econometric modelling. It is likely that we will try several specifications or different methods, resulting in multiple versions. Previously, I created separate folders for each version and added the date to the folder name. However, since we are now using Git, I will commit changes after every analysis step or when processed data is added to the project. This way, if something goes wrong, I can always revert back.*

  - List possible strategies you might use to document your data throughout your project.

  *I use a `csv` file in the `data-raw/` folder to document where and when I obtained each piece of raw data. Processed data will be placed in the `data/` folder to keep it separate from the raw data. Additionally, a `README` text file will be created in the data folder to explain any intermediate data if needed.*
