---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

_This repository is an activity completed by [Zehui Yin](https://zehuiyin.github.io/) for the course [GEOG 712 Reproducible Research Workflow with GitHub and R](https://academiccalendars.romcmaster.ca/preview_course.php?catoid=55&coid=274877), taught by [Dr. Antonio Paez](https://experts.mcmaster.ca/display/paezha) in Fall 2024._

# Research Interest

My research interests lie in __spatial analysis__, __travel behaviour__, __public transit__, and __shared mobility__. I am particularly interested in using an _evidence-based approach_ and _quantitative methods_, such as _econometrics_, to examine transportation systems. From 2022 to 2024, I worked as a research assistant in the [Suburban Mobilities Cluster](https://www.utsc.utoronto.ca/suburban-mobilities/) within the Department of Human Geography at the University of Toronto Scarborough. During this time, I conducted _surveys_ and _network_ data analysis to explore transportation _accessibility_, _equity_, and _justice_ in suburban areas, particularly in Scarborough, Ontario, under the supervision of [Dr. Steven Farber](https://www.utsc.utoronto.ca/geography/steven-farber), [Dr. Andre Cire](https://utsc.utoronto.ca/mgmt/andre-cire), and [Dr. Ignacio Tiznado-Aitken](https://tiznadoaitken.cl/). My works on analyzing transport investment priorities among Scarborough residents and cycling comfort levels on different street types in Toronto were both funded by the [University of Toronto Excellence Award](https://www.utsc.utoronto.ca/research/university-toronto-excellence-award). I have also collaborated on several shared micromobility projects with [Dr. Xiang Yan](https://www.essie.ufl.edu/people/name/xiang-yan/) from the University of Florida. In these projects, I conducted econometric modelling and spatial analysis to investigate the travel behaviour and spatiotemporal patterns of shared e-scooter usage in Washington, DC, and Los Angeles.

# Favourites

## Favourite Music

<!---
Generated using https://www.tablesgenerator.com/
--->

1. Like the Wind (Simplified Chinese: 像风一样) by Joker Xue (Simplified Chinese: 薛之谦)
2. Express Your Feelings (Simplified Chinese: 聊表心意) by Sara (Xijun) Liu (Simplified Chinese: 刘惜君) and Joker Xue (Simplified Chinese: 薛之谦)
3. The City (Simplified Chinese: 牧马城市) by Buyi Mao (Simplified Chinese: 毛不易)
4. The Brightest Star in the Night Sky (Simplified Chinese: 夜空中最亮的星) by Escape Plan (Simplified Chinese: 逃跑计划)
5. The Final Battle (Simplified Chinese: 最后的战役) by Jay Chou (Simplified Chinese: 周杰伦)

## Favourite Equation

The equation below shows the OLS estimators in matrix form.

$$
\hat{\beta}=(X'X)^{-1}X'y
$$

## Favourite Artists

| Name              | Achievements              |
|-------------------|---------------------------|
| Vincent van Gogh  | The Starry Night          |
| Pablo Picasso     | Guernica                  |
| Leonardo da Vinci | Mona Lisa                 |
| Johannes Vermeer  | Girl with a Pearl Earring |
| Claude Monet      | Impression, Sunrise       |

# A Chunk of Code

```{r}
# run a linear regression with the built-in dataset mtcars
m1 <- lm(mpg ~ cyl + hp + wt + vs + am, 
         data = mtcars)

# save the model results to data folder
saveRDS(m1, file = "./data/m1.rds")


# summarize the regression results
summary(m1)
```

# Folder Structure
<!---
Generated using https://tree.nathanfriend.io

Text used:

- data
  - ...
- data-raw
  - data_source.csv
  - Transit_Service_Areas.geojson
- images
  - toronto_crime.png
- renv
  - ...
- _dependencies.R
- my-GEO712-repository.Rproj
- README.md
- README.Rmd
- renv.lock
- ...
--->

```
.
├── data/
│   └── ...
├── data-raw/
│   ├── data_source.csv
│   └── Transit_Service_Areas.geojson
├── images/
│   └── toronto_crime.png
├── renv/
│   └── ...
├── _dependencies.R
├── my-GEO712-repository.Rproj
├── README.md
├── README.Rmd
├── renv.lock
└── ...
```

The folder structure is illustrated in the diagram above.

- The `data/` folder stores processed data after analysis or cleaning.
- The `data-raw/` folder contains read-only raw data for the project. Within this folder,`data_source.csv` is a data table that includes the source information for all raw data, such as the download URL and the access date.
- The `images/` folder is designated for storing images, figures, and photos.
- The `_dependencies.R` file is used to add packages to the lockfile that are not automatically included.
